Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-18

### 2016-02-19 ec-2016/source/paper.tex
Add subsection:Trust.

Scale and indirect communication

>>>>

The sparsity requirement has an important consequence for network infrastructure:
as a network grows, the number of nodes will exceed the number of links a given
node can support and many pairs of nodes will only be indirectly connected,
with all paths between them passing through at least one intermediary node.
These intermediary nodes are targets for potential attacks.
More specifically, the threat model is as follows: Alice sends a message to
Bob via one or more intermediaries, but those intermediaries may either block
or alter the message.
The ability to tolerate these types of adversarial attacks often depends on
Alice and Bob's ability to assume that some nodes have not been
compromised---to {\em trust} them.

Web of trust and transitivity.

\section{Partial Trust}
